Carbonate chemistry at Ny-Ålesund

### 2021-06-27 awipev-CO2.Rmd
test

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
  odt_document: default
---
![ ](Images/AWIPEV-Logo.jpg){width=250px}

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
  odt_document: default
---
![ ](Images/AWIPEV-Logo.jpg){width=250px}
#test
